---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Science? Make It Spatial

This is a talk given by Angela Li of the [Center for Spatial Data Science (CSDS)](https://spatial.uchicago.edu) at UChicago for [DC R Conference 2018](https://rstats.ai). The goal was to introduce spatial analysis methods to a crowd that was deeply familiar with R, but new to spatial analysis.

Below are the slides from the talk. The shortlink to the slides is [bit.ly/dc-spatial](bit.ly/dc-spatial) for easy reference.

```{r echo = FALSE}
knitr::include_url('https://angela-li.github.io/slides/2018-11-08/dc-r-presentation#1')
```

## References
Thanks to [Garrick Aden-Buie](https://github.com/gadenbuie) for the [`xaringanthemer`](https://github.com/gadenbuie/xaringanthemer) package. 

Note: For exporting xaringan slides to a PDF, I used the `webshot` package, instructions for which are found in the [xaringan wiki](https://github.com/yihui/xaringan/wiki/Export-Slides-to-PDF).

## Contact Me
Feel free to email me at ali6@uchicago.edu or reach out [on Twitter](https://twitter.com/CivicAngela).